Astronomical Image colorization and up-scaling with generative adversarial networks

### 2022-09-23 Research Paper/iclr2022/Astronimical_Image_Colorization_and_upscaling.tex
Add ml.astro paper

\documentclass{article} % For LaTeX2e
\usepackage{iclr2022_conference,times}

@@

\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.  Funding acknowledgements go at the end of the paper.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213, USA \\
\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
\And
Ji Q. Ren \& Yevgeny LeNet \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email}
}

@@

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}
\usetikzlibrary{chains, calc,fit}

@@

The problem of colorization of gray scale images with an automated algorithm has been under much research within the machine learning and computer vision communities. Beyond simply being fascinating from an aesthetic and artificial intelligence perspective, such capability has broad practical applications. It is an area of research that possesses great potentials in applications: from black and white photo reconstruction, image augmentation, image enhancement to video restoration for improved interpretability. 
    Image downscaling is an innately lossy process. The principal objective of super resolution imaging is to reconstruct a low resolution image into a high resolution one based on a set of low-resolution images to rectify the limitations that existed while the procurement of the original low-resolution images. This is to insure better visualization and recognition for either scientific or non-scientific purposes. Even if an upscaling algorithm is particularly good, there will always be some data loss from high frequency due to a downscale-upscale function performed on the image. Ultimately, even the best upscaling algorithms are unable to effectively reconstruct data that does not exist. Conventional methods for image upscaling rely on low-information and a smooth interpolation between known pixels. Thes methods can effectively be treated as a convolution with a kernel which encodes no information about the original image. The problem, has one of it's solutions as and can be solved by using Generative Adversarial Networks (GANs) to hallucinate high frequency data in a super scaled image that does not exist in the smaller image. Even though they increase the resolution of an image, they do not achieve the desired clarity in the super-resolution task. By using the above mentioned method, not a perfect reconstruction can be obtained albeit instead a rather plausible guess can be made at what the lost data might be, constrained to reality by a loss function penalizing deviations from the ground truth image.\\ 
    \begin{figure}[!htb]
    	\centering
    	\begin{subfigure}[b]{0.4\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{figures/samples_main}
    		\caption{Ground Truth}
    		\label{fig: main_color_samples}
    	\end{subfigure}
    		\hspace{0.1 in}
    	\begin{subfigure}[b]{0.4\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{figures/samples_full-trained}
    		\caption{ResNet18 Full trained L*a*b}
    		\label{fig: resnet18_full}
    	\end{subfigure}
    	\caption{Results of fine-tuned ResNet18 in L*a*b colorspace compared with ground truth images}
    \end{figure}

As noted in \citep{Gao2019astronomical}, a huge number of raw images are present unprocessed and unnoticed in the Hubble Legacy Archives. These raw images are typically black and white, low-resolution and unfit to be shared with the world. It takes huge amounts of hours to process them. This processing is necessary because it's difficult for astronomers to distinguish objects from the raw images. The processing is further made necessary owing to noise from other bodies in the universe, changing optical characteristics in the system and random \& synthetic noise from the sensors in the telescope. Furthermore, for the process of highlighting small features that ordinarily wouldn't be able to be picked out against noise of the image, we need colorization. The processing of the images is so time consuming that the images are rarely seen by human eyes. Not only is new data being continuously produced by Hubble Telescope, but new telescopes are soon to come online. This goes to show that the problem will likely get worse. A simplification of image processing by using artificial image colorization and super-resolution can be done in an automated fashion to make it easier for astronomers to visually identify and analyze objects in Hubble dataset.
    \begin{figure}[!htb]
    	\centering
    	\begin{subfigure}[b]{0.2\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{figures/original_sample}
    		\caption{Original image}
    		\label{fig: original_sample}
    	\end{subfigure}
    	\begin{subfigure}[b]{0.2\textwidth}
    		\centering
    		\includegraphics[width=\textwidth]{figures/GAN_output_sample}
    		\caption{GAN output}
    		\label{fig: gan_output_sample}
    	\end{subfigure}
    	\caption{Fig \ref{fig: original_sample} is the original image and fig \ref{fig: gan_output_sample} is the image produced by our GAN}
    	\label{fig: sample_comp}
    \end{figure}

\section{Literature Review}
\subsection{Image Colorization}
\subsubsection{Hint Based Colorization}
\hspace*{0.25 in}\citet{levin2004colorization} proposed using colorization hints from the user in a quadratic cost function which imposed that neighboring pixels in space-time with similar intensities should have similar colours. This was a simple but effective method but only had hints which were provided in form of imprecise colored scribbles on the grayscale input image. But with no additional information about the image, the method was able to efficiently generate high quality colorizations. \cite{huang2005edge} addressed the color bleeding issue faced in this approach and solved it using adaptive edge detection. \cite{yatziv2006chrominance} used luminescence based weighting for hints to boost efficiency. \cite{qu2006manga} extended the original cost function to apply color continuity over similar textures along with intensities.

\subsubsection{Deep Colorization}
\hspace*{0.25 in}Owing to recent advances, the Convolutional Neural Networks are a de facto standard for solving image classification problems and their popularity continues to rise with continual improvements. CNNs are peculiar in their ability to learn and differentiate colors, patterns and shapes within an image and their ability to associate them with different classes.\\
    \hspace*{0.25 in}\cite{cheng2016deep} proposed a per pixel training for neural networks using DAISY \citep{tola2008descriptor}, and semantic \citep{long2015semantic} features to predict the chrominance value for each pixel, that used bilateral filtering to smooth out accidental image artifacts. With a large enough dataset, this method proved to be superior to the example based techniques even with a simple Euclidean loss function against the ground truth values.\\
\hspace*{0.25 in}Finally, \cite{dahl2016automatic} successfully implemented a system to automatically colorize black \& white images using several ImageNet-trained layers from VGG-16 \citep{simonyan2015deep} and integrating them with auto-encoders that contained residual connections. These residual connections merged the outputs produced by the encoding VGG16 layers and the decoding portion of the network in the later stages. \cite{he2015deep} showed that deeper neural networks can be trained by reformulating layers to learn residual function with reference to layer inputs. Using this \textit{Residual Connections}, \cite{he2015deep} created the \textit{ResNets} that went as deep as 152 layers and won the 2015 ImageNet Challenge.\\

\subsubsection{Generative Adversarial Networks}
\hspace*{0.25 in}\cite{goodfellow2014generative} introduced the adversarial framework that provides an approach to training a neural network which uses the generative distribution of $p_g(x)$ over the input data $x$.\\
    \hspace*{0.25 in}Since it's inception in 2015, many extended works of GAN have been proposed over years including DCGAN \citep{radford2016unsupervised}, Conditional-GAN \citep{mirza2014conditional}, iGAN \citep{zhu2018generative}, Pix2Pix \citep{isola2018imagetoimage}.\\
    \hspace*{0.25 in}\cite{radford2016unsupervised} applied the adversarial framework for training convolutional neural networks as generative models for images, demonstrating the viability of \textit{deep convolutional generative adversarial networks}.\\
    \hspace*{0.25 in}DCGAN is the standard architecture to generate images from random noise. Instead of generating images from random noise, Conditional-GAN \citep{mirza2014conditional} uses a condition to generate output image. For e.g. a grayscale image is the condition for colorization of image. Pix2Pix \citep{isola2018imagetoimage} is a Conditional-GAN with images as the conditions. The network can learn a mapping from input image to output image and also learn a separate loss function to train this mapping. Pix2Pix is considered to be the state of the art architecture for image-image translation problems like colorization.

\subsection{Image Upscaling}
\subsubsection{Frequency-domain-based SR image approach}
\hspace*{0.25 in} \cite{tsai1984multiframe} proposed the frequency domain SR method, where SR computation was considered for the noise free low resolution images. They transformed the low resolution images into Discrete Fourier transform (DFT) and further combined it as per the relationship between the aliased DFT coefficient of the observed low resolution image and that of unknown high resolution image. Then the output is transformed back into the spatial domain where a higher resolution is now achieved.\\
    \hspace*{0.25 in} While Frequency-domain-based SR extrapolates high frequeny information from the low resolution images and is thus useful, however they fall short in real world applications.\\
\subsubsection{The interpolation based SR image approach}
\hspace*{0.25 in} The interpolation-based SR approach constructs a high resolution image by casting all the low resolution images to the reference image and then combining all the information available from every image available.
    The method consists of the following three stages
    (i) the registration stage for aligning the low-resolution input images,
    (ii) the interpolation stage for producing a higher-resolution image, and
    (iii) the deblurring stage which enhances the
    reconstructed high-resolution image produced in the step (ii).

@@

\subsubsection{Regularization-based SR image approach}
\hspace*{0.25 in} Most known Bayesian-based SR approaches are maximum likelihood (ML) estimation approach  and maximum a posterior (MAP) estimation approach.\\
    \hspace*{0.25 in}  While \cite{Brian1996ML} proposed the first ML estimation based SR approach with the aim to find the ML estimation of high resolution image, some proposed a MAP estimation approach. MAP SR tries to takes into consideration the prior image model to reflect the expectation of the unknown high resolution image.\\

\subsubsection{Super Resolution - Generative Adversarial Networks (SR-GAN)}
\hspace*{0.25 in} The Genrative Adversarial Network \citep{goodfellow2014generative}, has two neural networks, the Generator and the Discriminator. These networks compete with each other in a zero-sum game.
    \cite{ledig2017photorealistic} introduced SRGAN in 2017, which used a SRResNet to upscale images with an upscaling factor of 4x. SRGAN is currently the state of the art on public benchmark datasets.

\section{Methodology}
    \subsection{Data collection}
    \hspace*{0.25 in}We started by scraping data off the Hubble Legacy Archive. The scrapper tool\footnote{Fork: https://github.com/obi-wan-shinobi/hla-scraper} which was used, courtesy of \cite{Gao2019astronomical}\footnote{Original repository: https://github.com/KMarshland/hla-scraper}, scraped off hundreds of thousands of colorized images the archive has available. The Hubble Legacy archive is slow and produces grainy images with lots of noise and majority are unprocessed. A filter for M101 (Messier 101) galaxy rendered more than 80 thousand images with a 1 degree difference between consecutive right ascension. The data acquired was large and there was no particularly efficient way to clean it without human investment. Cleaning tens of thousands of images by handpicking noiseless and well colored images is time consuming. For training the SRGAN, high resolution and well colored images were needed.\\
    \hspace*{0.25 in}Consequently, we scraped the Hubble Heritage project instead. The Hubble Heritage project releases the highest-quality astronomical images. They are all stitched together, colorized and processed to eliminate noise. Hubble Heritage then selects the best, most striking of these for public release. However, there were only $\sim150$ of these images that are actually useful. We scraped images from the main Hubble website as well so as to increase the amount of data we had. This provided another $\sim1000$ images approx. Limited by our computational resources, it was decided that the images will be in the dimensions of $256\times 256$ pixels and contains 3 channels namely Red, Green, Blue (RGB).\\

    \subsection{Image Color Space}
    \hspace*{0.25 in}An RGB image is essentially a rank 3 tensor of height, width and color where the last axis contains the color data of our image. The data is represented in RGB color space which has 3 numbers for every pixel indicating the amount of \textit{Red, Green, and Blue} values the pixel has.
    \begin{figure}[!htb]
    \begin{center}
    	\includegraphics[width=\textwidth]{figures/rgb_colorspace}
    	\caption{Reg, Green and Blue channels of an image (Main image by \href{https://unsplash.com/@aznbokchoy}{Lucas Benjamin})}
    	\label{rgb_colorspace}
    \end{center}
    \end{figure}
    In \textbf{L*a*b} color space, we have three numbers for each pixel but these numbers have different meanings.L, the first channel, has the \textbf{Lightness} of each pixel encoded and when we visualize this channel it appears as a black and white image. 
    \begin{figure}[!htb]
    \begin{center}
    	\includegraphics[width=\textwidth]{figures/Lab_colorspace}
    	\caption{Lightness, *a and *b channels of the L*a*b colorspace}
    	\label{lab_colorspace}
    \end{center}
    \end{figure}
    The \textbf{*a and *b} channels encode in them exactly how much \textbf{green-red} and \textbf{yellow-blue} each pixel is, respectively.
    \cite{guadarrama2017pixcolor,isola2018imagetoimage} propose the use of L*a*b color space instead of RGB to train the models. Intuitively, to the train a model for colorization, a grayscale image should be fed to it and we hope that it colors it. In the L*a*b colorspace, the model is fed the L channel, which is essentially a grayscale image, and we perform computations to predict the other two channels (*a and *b). After the predictions, we concatenate the channels and get a colorful image. In case of RGB, there is a need to explicitly convert the three channels down to 1 to make it a grayscale image and then feed it to the network hoping that it predicts three numbers per pixel. This is an unstable task due to sheer increase in volume of combinations from two numbers to three.

    We train models using both color spaces and compare their performance.
    \subsection{Mathematical Model}
    \subsubsection{Generative Adversarial Networks}
     A generative network, $G$, is supposed to learn the underlying distribution of a latent space, Y. Instead of visually assessing the quality of network outputs and judge how we can adapt the network to produce convincing results, we incorporate automatic tweaking during training by introducing a discriminative network $D$. The network D takes in both the fabricated outputs generated by G and real inputs from the underlying distribution Y. The network produces a probability of the image belonging to the real or fabricated space.
    \begin{figure}[!htb]
        \centering
        \resizebox{\textwidth}{!}{
        \input{figures/tex_files/gan_visualization.tex}}
        \caption{Approach for image colorization using conditional GANs. A sample grayscale image is provided as an input to the generator and the generated image along with the ground truth is fed to the discriminator. The probability \textit{p} is the probability that the discriminator thinks the two images are similar.}
        \label{fig:gan_visualization}
    \end{figure}
      Let $x \in X$ be a low resolution or a grayscale image and $y \in Y$ be it's underlying distribution from the latent space Y. Generator $G$ takes in input $x$ and produces an output $\hat{y}$. We define the mapping $x \rightarrow \hat{y}$ in the following manner:
      $$G(x) = \hat{y}$$

     The discriminative network D is fed the fabricated mapping $x \rightarrow \hat{y}$ and the underlying distribution of $x$ i.e. $y \in Y$. The network D then produces a result that is a probability distribution of the input space indicating the class of the image that it thinks the input belongs to. We define this as:
     $$D\big(G(x),y\big) = p$$
     where $p \in (0,1)$ is the probability that the image is fabricated or real.
    With conditional GAN, both generator and discriminator are conditioning on the input $x$. Let the generator be parameterized by $\theta_g$ and the discriminator be parameterized by $\theta_d$. The minimax objective function can be defined as:
    	\begingroup\makeatletter\def\f@size{7}\check@mathfonts \[
    		\min_{\theta_g}\max_{\theta_d}\Big[\mathbb{E}_{x,y\sim p_{data}} \log D_{\theta_d}(x,y) + E_{x\sim p_{data}} \log(1 - D_{\theta_d}(x, G_{\theta_g}(x))\Big]
    	\] \endgroup
        \normalsize
    Where, $G_{\theta_{g}}$ is the output of the generator and $D_{\theta_d}$ is the output of the discriminator.
    We're currently not introducing any noise in our generator to keep things simple for the time being. Also, we consider $L1$ difference between input $x$ and output $y$ in generator. On each iteration, the discriminator would maximize $\theta_d$ according to the above expression and generator would minimize $\theta_g$ in the following way:
    	\[
    		\min_{\theta_g}\Big[-\log(D_{\theta_d}(x,G_{\theta_g}(x)))+\lambda \Vert G_{\theta_g}(x) - y \Vert_1 \Big]
    	\]

@@

    \hspace*{0.25 in}\cite{isola2018imagetoimage} proposed a general solution to many image-to-image translation tasks. We propose a similar methodology as proposed in the paper with a few minor tweaks, so as to significantly reduce the amount of training data needed and minimize the training time to achieve similar results. Initially, we propose the use of a U-net for the generator. A pre-trained ResNet-18 network was used as the \textit{encoder} for the U-net with half of it's layers clipped off so as to get feature abstractions of the intermediate layers. \cite{ledig2017photorealistic} showed that training the generator separately in a supervised, deterministic manner helps it generalize the mapping from the input space to outputs. The idea solves the problem of \textit{"The blind leading the blind"} that is persistent in most image-to-image translation tasks to date. \\
    \hspace*{0.25 in}We pre-train our generator independently using the imagenet weights over the Common Objects in Context (COCO) dataset. Unlike adversarial training, this phase was supervised and the loss function used was \textit{mean absolute error} or the \textit{L1 Norm} from the target image. Though trained deterministically,the problem of rectifying incorrect predictions still persists due to constraints over the convergence of loss metric. To combat this, this trained generator was trained once again in an adversarial fashion to help generalize it further. We hypothesize that re-training in an adversarial fashion will further rectify the subtle color differences that \textit{mae} couldn't solve.\\

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{iclr2022_conference,times}
\pagestyle{plain} % removes running headers

@@

\author{Shreyas Kalvankar, Hrushikesh Pandit, Pranav Parwate, Atharva Patil \& Snehal Kamalapur \\
Department of Computer Engineering\\
K. K. Wagh Institute of Engineering Education and Research\\
Nashik, Maharashtra, India \\
\texttt{\{shreyas.kalvankar, hrushikesh.pandit\}@kkwagh.edu.in} \\
\texttt{\{pranav.parwate, atharva.patil, smkamalapur\}@kkwagh.edu.in} \\
}

@@

\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}
\usetikzlibrary{chains, calc,fit}

@@

Colorization of gray scale images with an automated algorithm has been under much research within the machine learning and computer vision communities. Beyond being fascinating from an aesthetic and artificial intelligence perspective, such capability has broad practical applications. It is an area of research that has untapped potential in applications: from black and white photo reconstruction, image augmentation, image enhancement to video restoration for improved interpretability. \\
\hspace*{0.167 in}Image downscaling is an innately lossy process. The principal objective of super resolution imaging is to reconstruct a low resolution image into a high resolution one based on a set of low-resolution images to rectify the limitations that existed while the procurement of the original low-resolution images, insuring better visualization and recognition for scientific and non-scientific purposes. A particularly good up-scaling algorithm will always have some data loss when producing high frequency image due to a downscale-upscale function. Ultimately, even the best up-scaling algorithms are unable to effectively reconstruct non-existing data. Conventional methods rely on low-information and a smooth interpolation between known pixels. These methods can effectively be treated as a convolution with a kernel which encodes no information about the original image. Generative Adversarial Networks (GANs) can be used to hallucinate high frequency data in a super scaled image that does not exist in the smaller image. Even after increasing the resolution, they fail to achieve the desired clarity in the task. By using the above mentioned method, not a perfect reconstruction can be obtained albeit instead a rather plausible guess can be made at what the lost data might be, constrained to reality by a loss function which penalizes deviations from the ground truth image.\\
    	\begin{subfigure}[b]{0.45\textwidth}
    		\includegraphics[width=\textwidth]{figures/samples_main}
    		\caption{Ground Truth}
    		\label{fig: main_color_samples}
    		\hspace{0.1 in}
    	\begin{subfigure}[b]{0.45\textwidth}
    		\includegraphics[width=\textwidth]{figures/samples_full-trained}
    		\caption{ResNet18 Full trained L*a*b}
    		\label{fig: resnet18_full}
    	\caption{Results of fine-tuned ResNet18 in L*a*b colorspace compared with ground truth images}
\hspace*{0.167 in}As noted in \cite{Gao2019astronomical}, a huge number of raw images are unprocessed and unnoticed in the Hubble Legacy Archives. These raw images, typically black and white, low-resolution, are unfit to be shared with the world. It takes huge amounts of hours to process them. This processing is necessary because it's difficult for astronomers to distinguish objects from the raw images and is further made necessary owing to noise from other bodies in the universe, changing optical characteristics in the system and random \& synthetic noise from the sensors in the telescope. Furthermore, for the process of highlighting small features that ordinarily wouldn't be able to be picked out against noise of the image, we need colorization. The processing of the images is so time consuming that the images are rarely seen by human eyes. Not only is new data being continuously produced by Hubble Telescope, but new telescopes are soon to come online. This goes to show that the problem will likely get worse. A simplification of image processing by using artificial image colorization and super-resolution can be done in an automated fashion to make it easier for astronomers to visually identify and analyze objects in Hubble dataset.
    	\begin{subfigure}[b]{0.3\textwidth}
    		\includegraphics[width=\textwidth]{figures/original_sample}
    		\caption{Original image}
    		\label{fig: original_sample}
    	\begin{subfigure}[b]{0.3\textwidth}
    		\includegraphics[width=\textwidth]{figures/GAN_output_sample}
    		\caption{GAN output}
    		\label{fig: gan_output_sample}
    	\caption{Fig \ref{fig: original_sample} is the original image and fig \ref{fig: gan_output_sample} is the image produced by our GAN}
    	\label{fig: sample_comp}

\section{Literature Review}
The following section presents a brief survey of existing research and methods explored to approach the problem.
\subsection{Image Colorization}
\subsubsection{Hint Based Colorization}
\hspace*{0.167 in}\citet{levin2004colorization} proposed using colorization hints from the user in a quadratic cost function which imposed that neighboring pixels in space-time with similar intensities should have similar colours. This was a simple but effective method but only had hints which were provided in form of imprecise colored scribbles on the grayscale input image. But with no additional information about the image, the method was able to efficiently generate high quality colorizations. \cite{huang2005edge} addressed the color bleeding issue faced in this approach and solved it using adaptive edge detection. \cite{yatziv2006chrominance} used luminescence based weighting for hints to boost efficiency. \cite{qu2006manga} extended the original cost function to apply color continuity over similar textures along with intensities.

\subsubsection{Deep Colorization}
\hspace*{0.167 in}Owing to recent advances, the Convolutional Neural Networks are a de facto standard for solving image classification problems and their popularity continues to rise with continual improvements. CNNs are peculiar in their ability to learn and differentiate colors, patterns and shapes within an image and their ability to associate them with different classes.\\
    \hspace*{0.167 in}\cite{cheng2016deep} proposed a per pixel training for neural networks using DAISY \citep{tola2008descriptor}, and semantic \citep{long2015semantic} features to predict the chrominance value for each pixel, that used bilateral filtering to smooth out accidental image artifacts. With a large enough dataset, this method proved to be superior to the example based techniques even with a simple Euclidean loss function against the ground truth values.\\
\hspace*{0.167 in}Finally, \cite{dahl2016automatic} successfully implemented a system to automatically colorize black \& white images using several ImageNet-trained layers from VGG-16 \citep{simonyan2015deep} and integrating them with auto-encoders that contained residual connections. These residual connections merged the outputs produced by the encoding VGG16 layers and the decoding portion of the network in the later stages. \cite{he2015deep} showed that deeper neural networks can be trained by reformulating layers to learn residual function with reference to layer inputs. Using this \textit{Residual Connections}, \cite{he2015deep} created the \textit{ResNets} that went as deep as 152 layers and won the 2015 ImageNet Challenge.\\

\subsubsection{Generative Adversarial Networks}
\hspace*{0.167 in}\cite{goodfellow2014generative} introduced the adversarial framework that provides an approach to training a neural network which uses the generative distribution of $p_g(x)$ over the input data $x$.\\
    \hspace*{0.167 in}Since it's inception in 2015, many extended works of GAN have been proposed over years including DCGAN \citep{radford2016unsupervised}, Conditional-GAN \citep{mirza2014conditional}, iGAN \citep{zhu2018generative}, Pix2Pix \citep{isola2018imagetoimage}.\\
    \hspace*{0.167 in}\cite{radford2016unsupervised} applied the adversarial framework for training convolutional neural networks as generative models for images, demonstrating the viability of \textit{deep convolutional generative adversarial networks}.\\
    \hspace*{0.167 in}DCGAN is the standard architecture to generate images from random noise. Instead of generating images from random noise, Conditional-GAN \citep{mirza2014conditional} uses a condition to generate output image. For e.g. a grayscale image is the condition for colorization of image. Pix2Pix \citep{isola2018imagetoimage} is a Conditional-GAN with images as the conditions. The network can learn a mapping from input image to output image and also learn a separate loss function to train this mapping. Pix2Pix is considered to be the state of the art architecture for image-image translation problems like colorization.

\subsection{Image Upscaling}
\subsubsection{Frequency-domain-based SR image approach}
\hspace*{0.167 in} \cite{tsai1984multiframe} proposed the frequency domain SR method, where SR computation was considered for the noise free low resolution images. They transformed the low resolution images into Discrete Fourier transform (DFT) and further combined it as per the relationship between the aliased DFT coefficient of the observed low resolution image and that of unknown high resolution image. Then the output is transformed back into the spatial domain where a higher resolution is now achieved.\\
    \hspace*{0.167 in} While Frequency-domain-based SR extrapolates high frequeny information from the low resolution images and is thus useful, however they fall short in real world applications.\\
\subsubsection{The interpolation based SR image approach}
\hspace*{0.167 in} The interpolation-based SR approach constructs a high resolution image by casting all the low resolution images to the reference image and then combining all the information available from every image available.
    The method consists of the following three stages
    (i) the registration stage for aligning the low-resolution input images,
    (ii) the interpolation stage for producing a higher-resolution image, and
    (iii) the deblurring stage which enhances the
    reconstructed high-resolution image produced in the step (ii).

@@

\subsubsection{Regularization-based SR image approach}
\hspace*{0.167 in} Most known Bayesian-based SR approaches are maximum likelihood (ML) estimation approach  and maximum a posterior (MAP) estimation approach.\\
    \hspace*{0.167 in}  While \cite{Brian1996ML} proposed the first ML estimation based SR approach with the aim to find the ML estimation of high resolution image, some proposed a MAP estimation approach. MAP SR tries to takes into consideration the prior image model to reflect the expectation of the unknown high resolution image.\\

\subsubsection{Super Resolution - Generative Adversarial Networks (SR-GAN)}
\hspace*{0.167 in} The Genrative Adversarial Network \citep{goodfellow2014generative}, has two neural networks, the Generator and the Discriminator. These networks compete with each other in a zero-sum game.
    \cite{ledig2017photorealistic} introduced SRGAN in 2017, which used a SRResNet to upscale images with an upscaling factor of 4x. SRGAN is currently the state of the art on public benchmark datasets.

\section{Methodology}
\begin{figure}[!htb]
        \centering
        \resizebox{\textwidth}{!}{
        \input{figures/tex_files/gan_visualization.tex}}
        \caption{Approach for image colorization using conditional GANs. A sample grayscale image is provided as an input to the generator and the generated image along with the ground truth is fed to the discriminator. The probability \textit{p} is the probability that the discriminator thinks the two images are similar.}
        \label{fig:gan_visualization}
    \end{figure}
\subsection{Data collection}
    \hspace*{0.167 in}We started by scraping data off the Hubble Legacy Archive\footnote{Based on observations made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble Legacy Archive, which is a collaboration between the Space Telescope Science Institute (STScI/NASA), the Space Telescope European Coordinating Facility (ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}. The scrapper tool\footnote{Fork: https://github.com/obi-wan-shinobi/hla-scraper} which was used, courtesy of \cite{Gao2019astronomical}\footnote{Original repository: https://github.com/KMarshland/hla-scraper}, scraped off hundreds of thousands of colorized images the archive has available. The Hubble Legacy archive is slow and produces grainy images with lots of noise and majority are unprocessed. A filter for M101 (Messier 101) galaxy rendered more than 80 thousand images with a 1 degree difference between consecutive right ascension. The data acquired was large and there was no particularly efficient way to clean it without human investment. Cleaning tens of thousands of images by handpicking noiseless and well colored images is time consuming. For training the SRGAN, high resolution and well colored images were needed.\\
    \hspace*{0.167 in}Consequently, we scraped the Hubble Heritage project instead. The Hubble Heritage project releases the highest-quality astronomical images. They are all stitched together, colorized and processed to eliminate noise. Hubble Heritage then selects the best, most striking of these for public release. However, there were only $\sim150$ of these images that are actually useful. We scraped images from the main Hubble website as well so as to increase the amount of data we had. This provided another $\sim1000$ images approx. Limited by our computational resources, it was decided that the images will be in the dimensions of $256\times 256$ pixels and contains 3 channels namely Red, Green, Blue (RGB).\\

    \subsection{Image Color Space}
\hspace{0.167 in}An RGB image is essentially a rank 3 tensor of height, width and color. The data is represented in RGB color space which has 3 numbers for every pixel indicating the amount of \textit{Red, Green, and Blue} values the pixel has. In \textbf{L*a*b} color space, we have three numbers for each pixel but these numbers have different meanings.L, the first channel, has the \textbf{Lightness} of each pixel encoded and when we visualize this channel it appears as a black and white image. 
    \begin{figure}[!htb]
    \centering
    \begin{subfigure}[b]{0.9\textwidth}
        \centering
    	\includegraphics[width=\textwidth]{figures/rgb_colorspace}
    	\caption{Reg, Green and Blue channels of an image (Main image by \href{https://unsplash.com/@aznbokchoy}{Lucas Benjamin})}
    	\label{rgb_colorspace}
    \end{subfigure}
    \begin{subfigure}[b]{0.9\textwidth}
        \centering
    	\includegraphics[width=\textwidth]{figures/Lab_colorspace}
    	\caption{Lightness, *a and *b channels of the L*a*b colorspace}
    	\label{lab_colorspace}
    \end{subfigure}
    \caption{Color spaces}
    \end{figure}
    The \textbf{*a and *b} channels encode in them exactly how much \textbf{green-red} and \textbf{yellow-blue} each pixel is, respectively.\\
\hspace*{0.167 in}\cite{guadarrama2017pixcolor,isola2018imagetoimage} proposed the use of L*a*b color space instead of RGB for the colorization task. Intuitively, to the train a model for colorization, a grayscale image should be fed to it and we hope that it colors it. In the L*a*b colorspace, the model is fed the L channel, which is essentially a grayscale image, and we perform computations to predict the other two channels (*a and *b). After the predictions, we concatenate the channels and get a colorful image. In case of RGB, there is a need to explicitly convert the three channels down to 1 to make it a grayscale image and then feed it to the network hoping that it predicts three numbers per pixel. This is an unstable task due to sheer increase in volume of combinations from two numbers to three. We train models using both color spaces and compare their performance.
    \subsection{Mathematical Model}
    Generative modeling uses Generative Adversarial Networks (GANs) for hallucinating an output vector space. A mathematical description is provided for a GAN below.
    \subsubsection{Generative Adversarial Networks}
\hspace*{0.167 in}A generative network, $G$, is supposed to learn the underlying distribution of a latent space, Y. Instead of visually assessing the quality of network outputs and judge how we can adapt the network to produce convincing results, we incorporate automatic tweaking during training by introducing a discriminative network $D$. The network D takes in both the fabricated outputs generated by G and real inputs from the underlying distribution Y. The network produces a probability of the image belonging to the real or fabricated space.\\
\hspace*{0.167 in}Let $x \in X$ be a low resolution or a grayscale image and $y \in Y$ be it's underlying distribution from the latent space Y. Generator $G$ takes in input $x$ and produces an output $\hat{y}$. We define the mapping $x \rightarrow \hat{y}$ in the following manner:
      $$G(x) = \hat{y}$$

\hspace*{0.167 in}The discriminative network D is fed the fabricated mapping $x \rightarrow \hat{y}$ and the underlying distribution of $x$ i.e. $y \in Y$. The network D then produces a result that is a probability distribution of the input space indicating the class of the image that it thinks the input belongs to. We define this as:
     $$D\big(G(x),y\big) = p$$
     where $p \in (0,1)$ is the probability that the image is fabricated or real.
\hspace*{0.167 in}With conditional GAN, both generator and discriminator are conditioning on the input $x$. Let the generator be parameterized by $\theta_g$ and the discriminator be parameterized by $\theta_d$. The minimax objective function can be defined as:
    	\begingroup\makeatletter\def\f@size{7}\check@mathfonts \[
    		\min_{\theta_g}\max_{\theta_d}\Big[\mathbb{E}_{x,y\sim p_{data}} \log D_{\theta_d}(x,y) + E_{x\sim p_{data}} \log(1 - D_{\theta_d}(x, G_{\theta_g}(x))\Big]
    	\] \endgroup
        \normalsize
    Where, $G_{\theta_{g}}$ is the output of the generator and $D_{\theta_d}$ is the output of the discriminator.
    We're currently not introducing any noise in our generator to keep things simple for the time being. Also, we consider $L1$ difference between input $x$ and output $y$ in generator. On each iteration, the discriminator would maximize $\theta_d$ according to the above expression and generator would minimize $\theta_g$ in the following way:
    	\[
    		\min_{\theta_g}\Big[-\log(D_{\theta_d}(x,G_{\theta_g}(x)))+\lambda \Vert G_{\theta_g}(x) - y \Vert_1 \Big]
    	\]

@@

    \hspace*{0.167 in}\cite{isola2018imagetoimage} proposed a general solution to many image-to-image translation tasks. We propose a similar methodology as proposed in the paper with a few minor tweaks, so as to significantly reduce the amount of training data needed and minimize the training time to achieve similar results. Initially, we propose the use of a U-net for the generator. A pre-trained ResNet-18 network was used as the \textit{encoder} for the U-net with half of it's layers clipped off so as to get feature abstractions of the intermediate layers. \cite{ledig2017photorealistic} showed that training the generator separately in a supervised, deterministic manner helps it generalize the mapping from the input space to outputs. The idea solves the problem of \textit{"The blind leading the blind"} that is persistent in most image-to-image translation tasks to date. \\
    \hspace*{0.167 in}We pre-train our generator independently using the imagenet weights over the Common Objects in Context (COCO) dataset. Unlike adversarial training, this phase was supervised and the loss function used was \textit{mean absolute error} or the \textit{L1 Norm} from the target image. Though trained deterministically,the problem of rectifying incorrect predictions still persists due to constraints over the convergence of loss metric. To combat this, this trained generator was trained once again in an adversarial fashion to help generalize it further. We hypothesize that re-training in an adversarial fashion will further rectify the subtle color differences that \textit{mae} couldn't solve.\\
    \hspace*{0.167 in}A pre-trained ResNet-50 with imagenet weights was used as the discriminator with last few layers clipped off. The discriminative network used is something called a "Patch Discriminator" proposed by \cite{isola2018imagetoimage}. In a \textit{vanilla} discriminator proposed by \cite{goodfellow2014generative}, the network produces a scalar output, representing the probability that the data $x$ belongs to the input distribution and not the generator distribution $p_g$. \cite{isola2018imagetoimage} proposed a modification to the discriminative network so as to produce, instead of a single scalar, a vector of probabilities representing different localities of the input distribution (image) $x$. For instance, a discriminator producing a $50 \times 50$ vector represents the probabilities every receptive field that is covered by the output vector. Thus, we can localize the corrections in the image that the generator should make.\\
    \hspace*{0.167 in}Finally, the trained generator and trained discriminator are fine-tune to fit on our data which is rather small in size compared to the previous datasets. These networks are trained in an adversarial fashion using the conditional GAN objective function \citep{isola2018imagetoimage} with some noise introduced as the L1 norm of generated image tensor to the target image tensor. The reason behind this is to train the generator using an adversarial component while trying to minimize the Manhattan distance between the generator output and target vector space.
